```{r misc, cache=cacheon}

check1 <- fn(wilcox.test(num_hsSod ~ natremia, data = edata %>% filter(natremia %in% c("Yes/Yes", "Yes/No")))$p.value, p = T, dig = 3)

check2 <- fn(wilcox.test(num_dcSod ~ natremia, data = edata %>% filter(natremia %in% c("Yes/Yes", "Yes/No")))$p.value, p = T, dig = 3)

check3ds <- edata %>%
  filter(natremia %in% c("Yes/Yes", "Yes/No")) %>%
  group_by(natremia) %>%
  summarise(
    med = fn(median(d_change_Sod), dig = 1),
    q1 = fn(quantile(d_change_Sod, probs = 0.25), dig = 1),
    q3 = fn(quantile(d_change_Sod, probs = 0.75), dig = 1),
    mean = fn(mean(d_change_Sod), dig = 1),
    sd = fn(sd(d_change_Sod), dig = 1)
  ) %>%
  mutate(out = paste0(med, " (", q1, "-", q3, ") / ", mean, " (", sd, ")")) %>%
  ungroup() %>%
  select(natremia, out)

check3p <- fn(wilcox.test(d_change_Sod ~ natremia, data = edata %>% filter(natremia %in% c("Yes/Yes", "Yes/No")))$p.value, p = T, dig = 3)
```

1. whether the difference in admission sodium between hyponatremia YES/YES (median admission sodium 131 mmol/L) and hyponatremia YES/NO group (median admission sodium 133) is statistically significant? Answer: p`r check1` (Mann-Whitney U test). 

2. what is the p-value for the difference in discharge sodium between hyponatremia YES/YES (median discharge sodium 132) and hyponatremia YES/NO group (median discharge sodium 138)? Answer: p`r check2` (Mann-Whitney U test). 

3. what was the median/mean change (delta) from admission to discharge in 1) hyponatremia YES/YES and 2) hyponatremia YES/NO group, and what is the p-value for the difference in delta (sodium change) between those two groups? Answer: The change (median (qi-q3) / mean (SD)) from admission to discharge sodium is `r check3ds %>% filter(natremia == "Yes/Yes") %>% pull(out)` (YES/YES) and 
`r check3ds %>% filter(natremia == "Yes/No") %>% pull(out)` (YES/NO) respectively with a difference of p`r check3p` (Mann-Whitney U test). 

4. in those, who were hyponatremic at admission, can we check if higher admission sodium is a predictor of correction of hyponatremia during hospitalization – in univariate and multivariate logistic regression – for multivariate using the variables from Table S2? Answer (I exchanged variables according to 5 below): 

```{r predsodium, cache=cacheon}

impdata <- miceadds::subset_datlist(imp, expr_subset = edata %>% mutate(koll = d_hsSod_cat == "<135") %>% pull(koll))

ormodcrude <- with(impdata, glm(formula(paste0("d_dcSod_cat == '>=135' ~ num_hsSod")),
  family = binomial(link = "logit")
))
sormodcrude <- summary(pool(ormodcrude))

ormodadj <- with(impdata, glm(formula(paste0("d_dcSod_cat == '>=135' ~ num_hsSod +", paste(predvarsmult, collapse = " + "))),
  family = binomial(link = "logit")
))
sormodadj <- summary(pool(ormodadj))

units <- 10

fixor <- function(mod, varname) {
  outor <- data.frame(
    logor = mod$estimate[2],
    lci = mod$estimate[2] - global_z05 * mod$std.error[2],
    uci = mod$estimate[2] + global_z05 * mod$std.error[2],
    p = fn(mod$p.value[2], dig = 3, p = TRUE)
  ) %>%
    mutate(orp = paste0(fn(exp(logor)^units, 2), " (", fn(exp(lci)^units, 2), "-", fn(exp(uci)^units, 2), "), ", p)) %>%
    # remove = Yes
    mutate(
      Variable = varname
    ) %>%
    select(Variable, orp)

  colnames(outor) <- c("Variable", "Odds Ratio (95% CI)")
  return(outor)
}

orc <- fixor(mod = sormodcrude, varname = "Sodium (units of 10) - Crude")
ora <- fixor(sormodadj, "Sodium (units of 10) - Adjusted")

orboth <- bind_rows(orc, ora)

default_kable(orboth,
  font_size = 8,
  caption = "Sodium as a predictor of amelioration of hyponatremia during hospitalization",
  scale_down = F
)
```

5. regarding predictors of correction of hyponatremia during hospitalization (Table S2) – can we please use “% change in systolic blood pressure (per 10% increase)” instead of “systolic blood pressure”, and “improvement in NYHA class (of at least 1 NYHA class) during hospitalization” instead of “NYHA class III/IV at discharge”? Also can we change the interval for “% change in weight” and “% change in eGFR” from “per 1%” to “per 10%”? Answer: Modifications made to Table \ref{tab:preddischarge}. Note that this change will effect all models using imputation since variables in the imputation model have changed. 

\clearpage

6. Could we provide a multivariate analysis of predictors of “de novo” hyponatremia during hospitalization? (i.e. development of hyponatremia [hyponatremia NO/YES] in patients with NO HYPONATREMIA at admission) – Including all parameters from Table S2 (after the above mentioned changes )? Answer:

```{r predhypo, cache=cacheon}

impdata <- miceadds::subset_datlist(imp, expr_subset = edata %>% mutate(koll = d_hsSod_cat == ">=135") %>% pull(koll))

ormod <- with(impdata, glm(formula(paste0("d_dcSod_cat == '<135' ~ ", paste(predvarsmult, collapse = " + "))),
  family = binomial(link = "logit")
))

sormod <- summary(pool(ormod))
nval <- length(sormod$term)

units <- rep(1, nval - 1)
units[sormod$term[2:nval] %in% c("num_age", "d_changepercent_CKDEPI", "d_changepercent_Bp1", "d_changepercent_weight")] <- 10
units[sormod$term[2:nval] %in% c("num_dmBmi", "num_dcEf")] <- 5

outor <- data.frame(
  var = as.character(sormod$term[2:nval]),
  logor = sormod$estimate[2:nval],
  lci = sormod$estimate[2:nval] - global_z05 * sormod$std.error[2:nval],
  uci = sormod$estimate[2:nval] + global_z05 * sormod$std.error[2:nval],
  p = fn(sormod$p.value[2:nval], dig = 3, p = TRUE)
) %>%
  mutate(orp = paste0(fn(exp(logor)^units, 2), " (", fn(exp(lci)^units, 2), "-", fn(exp(uci)^units, 2), "), ", p)) %>%
  # remove = Yes
  mutate(
    Variable = str_replace(var, fixed("Yes"), ""),
    Variable = paste0(Variable, " (units of ", units, ")"),
    Variable = str_replace(Variable, fixed(" (units of 1)"), "")
  ) %>%
  select(Variable, orp)

colnames(outor) <- c("Variable", "Odds Ratio (95% CI)")

write.xlsx(outor,
  paste0(
    "./output/tabs/Predictors of de novo hyponatremia during hospitalization_",
    Sys.Date(), ".xlsx"
  ),
  rowNames = FALSE, overwrite = T
)

default_kable(outor,
  font_size = 8,
  caption = "Predictors of de novo hyponatremia during hospitalization",
  scale_down = F
)
```

\clearpage

7. The Reviewer than states: “Given the above comments, I think that models for corrected hyponatremia or progression to hyponatremia should also use serum sodium as a continuous variable to verify that similar predictors are obtained”.
Answer: I prepared the same models as in Table \ref{tab:preddischarge} and Table \ref{tab:predhypo} but included sodium at admission. Note that the corrected hyponatremia model is the same as the adjusted model in Table \ref{tab:predsodium}. 

```{r preddischargesodium, cache=cacheon}

impdata <- miceadds::subset_datlist(imp, expr_subset = edata %>% mutate(koll = d_hsSod_cat == "<135") %>% pull(koll))

ormod <- with(impdata, glm(formula(paste0("d_dcSod_cat == '>=135' ~ num_hsSod + ", paste(predvarsmult, collapse = " + "))),
  family = binomial(link = "logit")
))

sormod <- summary(pool(ormod))
nval <- length(sormod$term)

units <- rep(1, nval - 1)
units[sormod$term[2:nval] %in% c("num_age", "d_changepercent_CKDEPI", "d_changepercent_Bp1", "d_changepercent_weight", "num_hsSod")] <- 10
units[sormod$term[2:nval] %in% c("num_dmBmi", "num_dcEf")] <- 5

outor <- data.frame(
  var = as.character(sormod$term[2:nval]),
  logor = sormod$estimate[2:nval],
  lci = sormod$estimate[2:nval] - global_z05 * sormod$std.error[2:nval],
  uci = sormod$estimate[2:nval] + global_z05 * sormod$std.error[2:nval],
  p = fn(sormod$p.value[2:nval], dig = 3, p = TRUE)
) %>%
  mutate(orp = paste0(fn(exp(logor)^units, 2), " (", fn(exp(lci)^units, 2), "-", fn(exp(uci)^units, 2), "), ", p)) %>%
  # remove = Yes
  mutate(
    Variable = str_replace(var, fixed("Yes"), ""),
    Variable = paste0(Variable, " (units of ", units, ")"),
    Variable = str_replace(Variable, fixed(" (units of 1)"), "")
  ) %>%
  select(Variable, orp)

colnames(outor) <- c("Variable", "Odds Ratio (95% CI)")

write.xlsx(outor,
  paste0(
    "./output/tabs/Predictors of amelioration of hyponatremia including sodium_",
    Sys.Date(), ".xlsx"
  ),
  rowNames = FALSE, overwrite = T
)

default_kable(outor,
  font_size = 8,
  caption = "Predictors of amelioration of hyponatremia during hospitalization including sodium",
  scale_down = F
)
```

```{r predhyposodium, cache=cacheon}

impdata <- miceadds::subset_datlist(imp, expr_subset = edata %>% mutate(koll = d_hsSod_cat == ">=135") %>% pull(koll))

ormod <- with(impdata, glm(formula(paste0("d_dcSod_cat == '<135' ~ num_hsSod + ", paste(predvarsmult, collapse = " + "))),
  family = binomial(link = "logit")
))

sormod <- summary(pool(ormod))
nval <- length(sormod$term)

units <- rep(1, nval - 1)
units[sormod$term[2:nval] %in% c("num_age", "d_changepercent_CKDEPI", "d_changepercent_Bp1", "d_changepercent_weight", "num_hsSod")] <- 10
units[sormod$term[2:nval] %in% c("num_dmBmi", "num_dcEf")] <- 5

outor <- data.frame(
  var = as.character(sormod$term[2:nval]),
  logor = sormod$estimate[2:nval],
  lci = sormod$estimate[2:nval] - global_z05 * sormod$std.error[2:nval],
  uci = sormod$estimate[2:nval] + global_z05 * sormod$std.error[2:nval],
  p = fn(sormod$p.value[2:nval], dig = 3, p = TRUE)
) %>%
  mutate(orp = paste0(fn(exp(logor)^units, 2), " (", fn(exp(lci)^units, 2), "-", fn(exp(uci)^units, 2), "), ", p)) %>%
  # remove = Yes
  mutate(
    Variable = str_replace(var, fixed("Yes"), ""),
    Variable = paste0(Variable, " (units of ", units, ")"),
    Variable = str_replace(Variable, fixed(" (units of 1)"), "")
  ) %>%
  select(Variable, orp)

colnames(outor) <- c("Variable", "Odds Ratio (95% CI)")

write.xlsx(outor,
  paste0(
    "./output/tabs/Predictors of de novo hyponatremia during hospitalization including sodium_",
    Sys.Date(), ".xlsx"
  ),
  rowNames = FALSE, overwrite = T
)

default_kable(outor,
  font_size = 8,
  caption = "Predictors of de novo hyponatremia during hospitalization including sodium",
  scale_down = F
)
```

\clearpage

8. Regarding the Cox models for long-term outcomes, can we please include “Daily dose of loop diuretic >40 mg equivalent furosemide dose at discharge” instead of “loop diuretic at discharge, yes vs no” in the analysis? Answer: See tables and figures for cox models. Note that this change will effect all models using imputation since variables in the imputation model have changed. 

9. Could we please provide individual p-values for in-hospital mortality for each hyponatremia group compared with the HYPONATREMIA NO/NO group? Answer: 

```{r inhospdeath4, cache=cacheon}

out <- data.frame(matrix(NA, ncol = 5, nrow = 3))
colnames(out) <- c("Model", levels(edata$natremia))

event <- "num_dcVital"
val <- "Dead"

## n (%)
out[1, 1] <- "n (%)"

ev <- edata %>%
  filter(!is.na(!!sym(event))) %>%
  group_by(natremia) %>%
  count(!!sym(event)) %>%
  mutate(
    per = fn(n / sum(n) * 100, 1),
    np = paste0(n, " (", per, "%)")
  ) %>%
  filter(!!sym(event) == val)

out[1, 2:5] <- paste0(
  ev$np
)

# log regressions

## crude

out[2, 1] <- "Crude OR (95% CI), p-value"

ormod <- with(imp, glm(formula(paste0(event, "=='", val, "' ~ relevel(natremia, ref = 'No/No')")),
  family = binomial(link = "logit")
))

sormod <- summary(pool(ormod))

out[2, 2:5] <- c(paste0(
  fn(exp(sormod$estimate[2:4]), dig = 2),
  " (", fn(exp(sormod$estimate[2:4] - global_z05 * sormod$std.error[2:4]), dig = 2),
  "-", fn(exp(sormod$estimate[2:4] + global_z05 * sormod$std.error[2:4]), dig = 2), "), ",
  fn(sormod$p.value[2:4], dig = 3, p = TRUE)
), "ref")

## adjusted individual covariates

out[3, 1] <- "Adjusted OR (95% CI), p-value"

ormod <- with(imp, glm(formula(paste0(event, "=='", val, "' ~ relevel(natremia, ref = 'No/No') + ", paste(logvars, collapse = " + "))),
  family = binomial(link = "logit")
))

sormod <- summary(pool(ormod))

out[3, 2:5] <- c(paste0(
  fn(exp(sormod$estimate[2:4]), dig = 2),
  " (", fn(exp(sormod$estimate[2:4] - global_z05 * sormod$std.error[2:4]), dig = 2),
  "-", fn(exp(sormod$estimate[2:4] + global_z05 * sormod$std.error[2:4]), dig = 2), "), ",
  fn(sormod$p.value[2:4], dig = 3, p = TRUE)
), "ref")

write.xlsx(out, paste0("./output/tabs/In-hospital death by Natremia_", Sys.Date(), ".xlsx"), rowNames = FALSE, overwrite = T)

default_kable(out,
  font_size = 6,
  caption = "In-hospital death by Natremia"
)
```
